Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-05-13 paper/related.tex
Add minor grammar and sentence structure changes
Fix et al in rw

EverCrypt from Protzenko et al is a library of verified cryptographic primitives including several state of art algorithms for computing digests \cite{9152808}.
Here the algorithms are specified in F* \cite{fstar}.
Automated proofs of properties of the crypto-primitives are done with a weakest-precondition calculus.
As subset of F* is compilable to C the library is compiled to different target backends.
The resulting library is performant and efficient.

@@

\cryptol\ has been used to formally verify different implementations of the same cryptographic algorithm in the past.
As a demonstration of \cryptol, Lewis \emph{et al} provided portions of the \emph{Advanced Encryption Standard} (AES) implemented in the language \cite{crypt-hi}.
The language has also been used to verify equivalence between Skein Hash algorithm implementations \cite{hard-soft}.
\cryptol\ is not limited to software, as Browning and Weaver \cite{design-verif} have shown that the language can be tuned to provide an abstraction of hardware.
They later provided a proof of equivalence between the FIPS AES specification and various optimized \cryptol\ implementations.
For certain tables, they initially demonstrated equivalence through mathematical principles.
These tables were also proven equivalent to less time-intensive statically defined tables used for the rest of their proofs.
As the OpenSSL implementation was highly optimized with similar static values, this paper mirrored the method Browning and Weaver outlined.
The language was also used to verify equivalence between the specification and hardware of the Verilog RTL's pseudorandom number generator \cite{pseudorandom}.

>>>>

EverCrypt from Protzenko \emph{et al.} is a library of verified cryptographic primitives including several state of art algorithms for computing digests \cite{9152808}.
Here the algorithms are specified in F* \cite{fstar}.
Automated proofs of properties of the crypto-primitives are done with a weakest-precondition calculus.
As subset of F* is compilable to C the library is compiled to different target backends.
The resulting library is performant and efficient.

@@

\cryptol\ has been used to formally verify several cryptographic algorithms in the past.
As a demonstration of \cryptol, Lewis \emph{et al} provided portions of the \emph{Advanced Encryption Standard} (AES) implemented in the language \cite{crypt-hi}.
The language has also been used to verify equivalence between Skein Hash algorithm implementations \cite{hard-soft}.
\cryptol\ is not limited to software, as Browning and Weaver \cite{design-verif} have shown that the language can be tuned to provide an abstraction of hardware.
They later provided a proof of equivalence between the FIPS AES specification and various optimized \cryptol\ implementations.
For certain tables, they initially demonstrated equivalence through mathematical principles.
These tables were also proven equivalent to less time-intensive statically defined tables used for the rest of their proofs.
As the OpenSSL implementation was highly optimized with similar static values, this paper mirrored the method Browning and Weaver outlined.
The language was also used to verify equivalence between the specification and hardware of the Verilog RTL's pseudorandom number generator \cite{pseudorandom}.
